\documentclass[a4paper]{article}

\usepackage{titlesec}
\usepackage[]{xcolor}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[none]{hyphenat}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={185mm,255mm},
 left=15mm,
 top=20mm,
 }
 \usepackage[defaultsans]{opensans}
 \tolerance=2000
 \emergencystretch=10pt


\titleformat{\section}
{\Large}{}{0.5em}{\bfseries\uppercase}[{\titlerule[0.1pt]}]


\titleformat{\subsection}
{\Large\bfseries}{\hspace{-0.25in}$\bullet$}{0.1em}{}
\titlespacing{\subsection}{0em}{1em}{0em}


\titleformat{\subsubsection}[runin]
{\bfseries}{$\circ$ }{0em}{}[:]
\titlespacing{\subsubsection}{0em}{0.25em}{0.5em}


\titleformat{\paragraph}
{\normalfont\normalsize}{}{0em}{$\circ$ }
\titlespacing{\paragraph}{0em}{0.25em}{0.4em}


\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    }

\urlstyle{same}

\renewcommand{\maketitle}
{
   
	    \begin{flushleft}
	            {
	                \huge\bfseries
	                \theauthor
	            }
                \hfill
                {
                \large\color{darkgray}
                \href{tel:+13437778126}{+1(343)777-8126}
                
                }

                {
                \large\color{darkgray}
                Robotics Engineer
                }
                \hfill
                {
                \large\color{darkgray}
                \href{mailto:akari103@uottawa.ca}{akari103@uottawa.ca}
                }
                
                {
                    \small\color{darkgray}
                    \faIcon{map-marker} 
                    % \href{https://goo.gl/maps/A45DLKTQPWSze1PK7}{6-65 Commanda Way, Ottawa K1M 1E7}
                    {\small\bfseries Ottawa}
                }
                \hfill
                \huge\href{http://www.linkedin.com/in/ali-karimzade}{{\faIcon{linkedin}}}
                \huge\href{http://github.com/ake1999}{{\faIcon{github}}}
	    \end{flushleft}  


}

\setlength{\columnsep}{4em}

\begin{document}
\pagenumbering{gobble}
\title{R\'esum\'e}
\author{Ali Karimzade}

\maketitle

\section{Summary of Qualifications}

\paragraph{MEng student at the University of Ottawa, honing expertise in robotics and applied AI.}
\paragraph{Currently spearheading a project on 3D mapping and efficient navigation using TurtleBot 3 and RGBD depth cameras.}
\paragraph{Accomplished in collaborative project management, adept with Git and Docker.}
\paragraph{Directed a groundbreaking thesis project to optimize robotic manipulators using deep reinforcement learning.}
\paragraph{Specialized in SLAM, path planning, and manipulator control within the robotics domain.}
\paragraph{Experienced lab instructor, skilled at demystifying complex robotics concepts.}
\paragraph{Proven track record of innovation and leadership in interdisciplinary teams.}


\section{Education}

\subsection{Master of Engineering, Mechanical Engineering (Robotics)}
{\bfseries\small University of Ottawa, Ontario}
\hfill
{\bfseries\small September 2022 - Present}
        
\subsubsection{Master's Project}
- Currently working on a cutting-edge project involving 3D mapping and navigation optimization using TurtleBot 3 and RealSense depth cameras. The aim is to enhance robotic navigation efficiency through advanced mapping techniques.
        
\subsubsection{Relevant Courses}
- Biomechanics of Movements
- Digital Signal Processing
- Applied Artificial Intelligence
- Mechatronics
- Machine Learning for Adaptive and Intelligent Control Systems
- Robotics
- Instrumentation Techniques (Audited)
- Adaptive Signal Processing (Audited)

\subsubsection{Overall GPA}
3.73(as of now)

\subsection{Bachelor of Science, Mechanical Engineering (Robotics)}
{\bfseries\small University of Isfahan, Isfahan}
\hfill
{\bfseries\small September 2016 - October 2020}
        
\subsubsection{Bachelor's Thesis}
\href{https://github.com/ake1999/aarm}{Using Deep Reinforcement Learning Algorithms to Control Robotic Manipulators} 
        
{\bfseries\small Supervisor: Dr. Karimpour}
\hfill
{\bfseries\small Grade: 20/20}
        
\subsubsection{Relevant Courses}
- Computer Programming
- Dynamics
- Dynamics of Mechanics
- Mechanical Vibration
- Automatic Control
- Robotics
- Artificial Intelligence and Expert Systems
- Simulation of Dynamic Systems and Control
- Digital Image Processing (Audited)
        
\subsubsection{Overall GPA}
3.46

\section{Skills}

\subsection{Technical Skills}
        
\subsubsection{Robotics}
- SLAM (Simultaneous Localization and Mapping)
- Path Planning
- Manipulator Control
- Motion Planning
- Pick and Place
    
\subsubsection{Digital Signal Processing}
- FIR and IIR Filters
- FMCW Radars
- Recursive Least Squares
- Adaptive Prediction
- Antenna Beamforming
    
\subsubsection{Control Systems}
- Lead-Lag and PID Controllers
- State-Space Controllers
- Optimal Control
- Reinforcement Learning
- Self-Tuning Regulators
    
\subsubsection{Machine Learning}
- Support Vector Machine (SVM)
- Random Forests
- Dimensionality Reduction
- CNN (Convolutional Neural Networks)
- RNN (Recurrent Neural Networks)
- Reinforcement Learning
    
\subsubsection{Computer Vision}
- Noise Filters
- Spectral Analysis
- Object Classification
    
\subsubsection{Embedded Systems}
- Raspberry Pi
- NVIDIA Jetson TX1
- Arduino

\newpage
\subsection{Software Skills}
        
\subsubsection{Robotics}
- Robot Operating System (ROS)
- Gazebo
- MoveIt
- MuJoCo
- OpenSim
- LabVIEW
    
\subsubsection{Machine Learning}
- TensorFlow
- PyTorch
- scikit-learn
    
\subsubsection{Computer Vision}
- OpenCV
- Matlab Image Processing Toolbox
    
\subsubsection{Operating Systems}
- Ubuntu
- Windows
- Debian
    
% \subsubsection{Web and Android Development}
% - Tailwind CSS
% - React
% - Django
% - SQL
% - Android Studio
    
\subsection{Programming and Markup Languages}
        
\subsubsection{Programming Languages}
- Python
- JavaScript
- C++
- Java
    
\subsubsection{Markup Languages}
- {\LaTeX}
- XML
- YAML
- JSON
- HTML
- CSS
% - SQL
    
\subsection{Soft Skills}
        
\subsubsection{Quick Learner}
Constantly keen to learn more, especially in my area of interest.
    
\subsubsection{Teamwork}
Proficient in collaborative projects, adept at using Git and Docker for efficient DevOps in teams.

\section{Research Interests}
\begin{multicols}{2}[]
    \begin{itemize}
        \itemsep0em 
        \item Machine Learning (Reinforcement learning)
        \item Control System Design
        \item Computer vision
        \item Robotics and Simulation
        \item Digital Signal Processing
        \item Embedded systems programming
    \end{itemize}
\end{multicols}


\section{Relevant Work Experience}
\subsection{Teacher Assistant in Robotics}
{\bfseries\small Laboratory Instructor — University of Ottawa, Ontario}
\hfill
{\bfseries\small MAY 2023 - Present}

\paragraph{Proficiently taught working with robots: TurtleBot3, OpenManipulator, Simulation of KUKA LBR iiwa.}
\paragraph{Effectively instructed ROS 1\&2, Gazebo simulation for control, manipulation, and navigation tasks.}
\paragraph{\href{https://github.com/ake1999/Robotics_Course_ROS_2023}{Demonstrated expertise in teaching MoveIt for pick and place and motion planning.}}
\paragraph{\href{https://github.com/ake1999/Mobile_Robotics_Course_ROS_2023}{Instructed SLAM and path planning with Navigation Stack and Nav 2 for autonomous mobile robots.}}
\subsection{Robotics Researcher}

{\bfseries\small Research Team Member — University Of Isfahan, Isfahan}
\hfill
{\bfseries\small JAN 2019 - JAN 2021}

\paragraph{Reconstruction of a homemade 3 DOF robot and servo motor drivers connection to Advantech PCI cards.}
\paragraph{\href{https://github.com/ake1999/aarm}{Operation of the robot with ROS and its simulation in the Gazebo software.}}
\paragraph{Development of a controller and motion planner for it in the ROS environment.}

\subsection{Computer Vision Engineer}
{\bfseries\small Internship — Novinilya Company, Isfahan}
\hfill
{\bfseries\small JUN 2019 - AUG 2019}
\nopagebreak
\paragraph{Examination of the surface quality of the parts on the mass production at the plants.}
\paragraph{Object recognition with embedded boards like Jetson TX1 and industrial Basler cameras in the company's R\&D team.}

\section{Academic Projects}

\subsection{Artificial Intelligence}

\paragraph{\href{https://github.com/ake1999/TD3_Ant_v4}{Twin Delayed DDPG (TD3) algorithm implementation for the Ant robot in MuJoCo (in Gym library) to run forward.}}
\paragraph{Evolutionary algorithms Implementation, including the Differential Evolution Algorithm (DE) and the \href{https://github.com/ake1999/MVO_MATLAB}{Multi-Verse Optimizer (MVO)}.}
\paragraph{\href{https://github.com/ake1999/aarm}{Implementation of DDPG and TD3 algorithms in my B.Sc. thesis to push objects to their desired goal in a simulated environment with the help of hindsight experience replay paper}.}
\paragraph{Implementation of deep Q-Networks in a four-player fruit-eating game for an AI competition.}
\paragraph{Using K-means and KNN in Scikit-Learn for the Classification of cities' weather as dry or humid using unlabeled data}
            
\newpage
\subsection{Image Processing and Computer Vision}

\paragraph{\href{https://github.com/ake1999/CNN_AlexNet}{Implementation of the AlexNet architecture for image classification on the MNIST and CIFAR-10 datasets.}}
\paragraph{Designing filters in the frequency and spatial domain in both OpenCV and MATLAB.}
\paragraph{Android software development to recognize chosen cap colors and program an Arduino board to sort plastic bottle caps.}

\subsection{Robotics}
            
\paragraph{Currently developing 3D maps using REALSENSE RGBD cameras with TurtleBot3 for homes and offices.}
\paragraph{Developed a line-following robot using an Android phone and Arduino for image processing.}
\paragraph{Simulated and controlled KUKA LBR iiwa in Gazebo using ROS controllers, implemented motion planning with MoveIt for pick and place tasks, and gained hands-on experience with the robot at Isfahan University of Technology (IUT).}
\subsection{Digital Signal Processing}
\paragraph{Implemented a noise canceling system using time domain multichannel FIR causal Wiener method for precise source extraction from acoustic mixtures.}
\paragraph{implemented a next frame video predictor utilizing the Wiener-Hopf solution, successfully reducing power in residual prediction error and enhancing video compression efficiency.}
\paragraph{\href{https://github.com/ake1999/FMCW_Radar_Ake}{FMCW radar simulation for autonomous vehicles to detect objects' movement within 300 meters.}}
\subsection{Systems and Controls}
\paragraph{Designing a PID controller for a simulated 3-DOF robot in ROS (used in the B.Sc. thesis).}
\paragraph{Using LabVIEW for the implementation of keyboard-based control with PID control.}
\paragraph{Torque control of servomotors, system identification, and PID/lead-lag controller design with MATLAB.}% \pagebreak
% \section{Honors \& Awards}
%     \paragraph{Among Exceptional Talents at the University of Isfahan (2020).}
%     \paragraph{Accepted in the provincial Chemistry Olympiad (2015).}
%     \paragraph{I was among the top twenty percent of students in the Mechanical Engineering Department (2020).}a
%     \paragraph{Achieve ranking of 5308 among 162879 participants in the University Entrance Examination for bachelor's degree (2016).}
%     \paragraph{Participate in Physics and Chemistry High School Lab competitions (2015).}
% \section{WorkshopsWorkshops \& Seminars}
%     \paragraph{Completed “\href{https://coursera.org/share/727feebde54da2fa7042a84ce71c53e7}{Mathematics for Machine Learning: Linear Algebra}” course in Coursera.}
%     \paragraph{Completed “Robotics: Vision Intelligence and Machine Learning” course in edX(free).}
%     \paragraph{Participated in a workshop to make airplane models (Aero-Star \& Kadet) in a group (in 2020).}
%     \paragraph{Participated in the “Design for Manufacture and Assembly (DFMA)” seminar (in 2019).}
%     \paragraph{Participated in the workshop “making composite materials by hand lay-up method” (in 2018).}
%     \paragraph{Participated in Glider-making competitions at Sharif University of Technology(SUT) in a group of three students (in 2018).}
\section{Languages}
    
\begin{multicols}{2}
	\subsection{Persian}
	\paragraph{\bfseries Native}
	\vfill\null
	\columnbreak
	\subsection{English}
	\subsubsection{IELTS Academic}
	{6.5 Overall}
	\hfill
	{\bfseries DEC 2021}
\end{multicols}

% \begin{multicols}{2}
\section{References}
\subsection{Dr. Amirhossein Monjazeb}
\paragraph{\bfseries Professor, Faculty of Engineering, University of Ottawa, Ontario}
\paragraph{\bfseries Master's Project Supervisor}

{\large\subsubsection{Tel} {\href{tel:+16132661854}{+1(613)266-1854}}}

\Large\href{mailto:amirhossein.monjazeb@uottawa.ca}{\faIcon{envelope}}
\Large\href{https://uniweb.uottawa.ca/members/5272/profile}{\faIcon{globe}}
\Large\href{https://www.linkedin.com/in/amirhossein-monjazeb-0041625b/?originalSubdomain=ca}{\faIcon{linkedin}}
    
\subsection{Dr. Hossein Karimpour}
\paragraph{\bfseries Professor, Department of Mechanical Engineering, University of Isfahan, Isfahan}
\paragraph{\bfseries Bachelor's Thesis Supervisor}

{\large\subsubsection{Tel} {\href{tel:+983137935603}{+98(313)793-5603}}}

\Large\href{mailto:h.karimpour@eng.ui.ac.ir}{\faIcon{envelope}}
\Large\href{http://eng.ui.ac.ir/~h.karimpour}{\faIcon{globe}}
\Large\href{https://www.linkedin.com/in/hossein-karimpour-38373811a}{\faIcon{linkedin}}


        
% \subsection{Dr. Martin Bouchard}

% \paragraph{Professor, School of Electrical Engineering and Computer Science at the University Of Ottawa}
% \subsubsection{Tel} {\large \href{tel:+16135625800}{+1(613)562-5800}}
        
% \Large\href{}{\faIcon{envelope}}
% \Large\href{https://www.eecs.uottawa.ca/~bouchard/}{\faIcon{globe}}
% \Large\href{https://uniweb.uottawa.ca/?lang=en#!/members/186}{\faIcon{user}}
% \subsection{Dr. Karshenas}

% \paragraph{Assistant Professor, Artificial Intelligence Department at the University Of Isfahan}
% \subsubsection{Tel} {\large \href{tel:+983137934534}{+98(313)793-4534}}
        
% \Large\href{mailto:h.karshenas@eng.ui.ac.ir}{\faIcon{envelope}}
% \Large\href{https://engold.ui.ac.ir/~h.karshenas}{\faIcon{globe}}
% \Large\href{https://ir.linkedin.com/in/hossein-karshenas-01102a55}{\faIcon{linkedin}}

% \subsection{Dr. Kazemi}

% \paragraph{Assistant Professor, Department of Electrical Engineering at the University Of Isfahan}
% \subsubsection{Tel} {\large\href{tel:+983137937010}{+98(313)793-7010}}
        
% \Large\href{mailto:m.kazemi@eng.ui.ac.ir}{\faIcon{envelope}}
% \Large\href{https://engold.ui.ac.ir/~m.kazemi}{\faIcon{globe}}
% \Large\href{https://ir.linkedin.com/in/mohammad-kazemi-602a2722}{\faIcon{linkedin}}
% \end{multicols}

\end{document}